---
title: "eda"
author: "Lauren Henderson"
date: "2024-07-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Set Up

```{r factor.dataset}
library(tidyverse)
npha_data <- NPHA_doctor_visits

npha_data <- mutate_all(npha_data, as.factor)

library(ggplot2)

library(rsample)
```

Exporing Variables:

Doctors Visited-

```{r}
npha_data %>% 
  ggplot(aes(x = `Number of Doctors Visited`)) +
  geom_bar()
glimpse(npha_data)
```
1: 0-1 doctors (least)
2: 2-3 doctors (most)
3: 4 or more doctors

Age

```{r}
npha_data %>% 
  ggplot(aes(x = Age)) +
  geom_bar()
glimpse(npha_data)
```
1: 50-65
2: 65-80

All data is within second group.

Physical Health

```{r}
npha_data %>% 
  ggplot(aes(x = `Phyiscal Health`)) +
  geom_bar()
glimpse(npha_data)
```

-1: NA
1: Excellent
2: Very Good
3: Good (Most)
4: Fair
5: Poor (Least)

Mental Health

```{r}
npha_data %>% 
  ggplot(aes(x = `Mental Health`)) +
  geom_bar()
glimpse(npha_data)
```

-1: NA
1: Excellent
2: Very Good
3: Good
4: Fair
5: Poor (Least)

Mental health issues are very uncommon among older generations; possibly more stigmatized among older generationns, rather than not existing.


Comparing Health to Demographics


Physical Health based on _

-gender

```{r}

```

